---
title: "Follow Up: Wakefield: Random Data Set (Part II)"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    theme: journal
    number_sections: true
---

Ulf suggested related data sets in this comment: http://goo.gl/H1RKsV.  I have added the `relate` function as well as a `relate` argument to `r_series` in version 0.2.0 of **wakefield**.  Here is a demonstration of some of the capabilities:

```{r, echo=FALSE, message=FALSE, warning=FALSE}
if (!require("pacman")) install.packages("pacman"); library(pacman)
p_load(dplyr, wakefield, tidyr, ggplot2)
```

First install the newst version of **wakefield**:

```{r, eval=FALSE}
if (!require("pacman")) install.packages("pacman"); library(pacman)
p_install_gh("trinker/wakefield")
p_load(dplyr, wakefield, tidyr, ggplot2)
```


# relate Argument

The `relate` has been added to `r_series`.  It allows the user to specify the relationship between columns.  May be be a named list of \code{c("operation", "mean", "sd")} or a short hand string of the form of `"fM_sd"` where:

- `f` is one of (+, -, *, /)
- `M` is a mean value
- `sd` is a standard deviation of the mean value 

For example you may use `relate = "*4_1"`.  If `relate = NULL` no relationship is generated between columns.  I will use the short hand string form here.

# Adjust Correlations

Use the `sd` command to adjust correlations.

```{r}
round(cor(r_series(grade, 8, 10, relate = "+1_2")), 2)
round(cor(r_series(grade, 8, 10, relate = "+1_0")), 2)
round(cor(r_series(grade, 8, 10, relate = "+1_20")), 2)
round(cor(r_series(grade, 8, 10, relate = "+15_20")), 2)
```

# Visualize the relationship:
## Example 1

```{r}
dat <- r_data_frame(12,
    name,
    r_series(grade, 100, relate = "+1_6")
) 

dat %>%
    gather(Time, Grade, -c(Name)) %>%
    mutate(Time = as.numeric(gsub("\\D", "", Time))) %>%
    ggplot(aes(x = Time, y = Grade, color = Name, group = Name)) +
        geom_line(size=.8) + 
        theme_bw()
```

## Exmple 2
```{r}
dat <- r_data_frame(12,
    name,
    r_series(grade, 100, relate = "-10_20")
) 

dat %>%
    gather(Time, Grade, -c(Name)) %>%
    mutate(Time = as.numeric(gsub("\\D", "", Time))) %>%
    ggplot(aes(x = Time, y = Grade, color = Name, group = Name)) +
        geom_line(size=.8) + 
        theme_bw()
```
    
    
## Exmple 3
```{r}
dat <- r_data_frame(12,
    name,
    r_series(grade, 100, relate = "*1.05_.01")
) 

dat %>%
    gather(Time, Grade, -c(Name)) %>%
    mutate(Time = as.numeric(gsub("\\D", "", Time))) %>%
    ggplot(aes(x = Time, y = Grade, color = Name, group = Name)) +
        geom_line(size=.8) + 
        theme_bw()
```

## Exmple 4
```{r}
dat <- r_data_frame(12,
    name,
    r_series(grade, 100, relate = "/1.5_.5")
) 

dat %>%
    gather(Time, Grade, -c(Name)) %>%
    mutate(Time = as.numeric(gsub("\\D", "", Time))) %>%
    ggplot(aes(x = Time, y = Grade, color = Name, group = Name)) +
        geom_line(size=.8) + 
        theme_bw()
```

